\ \normalfont \normalsize \textsc{STK9101SP} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Project on Survival Analysis \\ \horrule{2pt} \\[0.5cm]

### 2016-11-29 latex/article.tex
more text

Our final model therefore contains age, bilirubin, and albumin, without any interactions. We therefore conclude that there is no evidence that the treatment has an effect on the patients.

\todo[inline]{Mention again that age could just be age\ldots}
\input{./tables/cox_final}

@@

@@

To test for inclusion of

>>>>

Our final model therefore contains age, bilirubin, and albumin, without any interactions. We therefore conclude that there is no evidence that the treatment has an effect on the patients.
\todo[inline]{Mention again that age could just be age\ldots}

In Table~\ref{tab:cox_final} and~\ref{tab:cox_final_ci} we show the resuting coefficients with confidence intervals and $p$-values. We see that the coefficient for age has not changes from the univariate case, while the coefficients for bilirubin and albumin has changed more. This probably because there is a stronger dependence between bilirubin and albumin.

\todo[inline]{Interpret coefficients}

\input{./tables/cox_final}

@@

In Table~\ref{tab:cox_time_dep} and~\ref{tab:cox_time_dep_log} we have tested the proportional hazard assumption of the model, using Schoenfeld-residuals. We see that non of the test indicate that there is a time dependency in the hazards. However, we find lowest $p$-values for the albumin covariate, so it could be interesting to further investigate this. This was, however, not pursued in this project.

@@

In Figure~\ref{fig:cox_full_linearity}, we have plotted the martingale residuals against the individual covariates. The residual seem to be evenly distributed around zero, suggesting that the functional form of our covariates are appropriate.
